---
title: "Vegetation Variation Between Islands"
author: "Finley O'Connor"
date: "2024-03-02"
output: html_document
---
#Loading data
```{r read-in-data, message = FALSE, warning=FALSE}
island_veg_all <- read_csv("island_veg_all.csv")
```


#Tidying?
This is counting how many species each PLOT has - this does not account for the `NA`s within the dataset, which will need to be addressed later. 
```{r}
island_veg_all_count <- island_veg_all %>%
  group_by(gps) %>% 
  count(spp) %>% 
  count(n) %>%
  mutate(spp_count = nn) %>% 
  select(-nn)

island_veg_all <- island_veg_all %>% 
                  left_join(island_veg_all_count, island_veg, by = "gps")
```

This is separating the data file into separate data frames by island?
```{r}
# Heron
heron_veg_all <- island_veg_all %>% 
  filter(location == "heron")

# Schoodic
schoodic_veg_all <- island_veg_all %>% 
  filter(location == "schoodic")

# shabby
shabby_veg_all <- island_veg_all %>% 
  filter(location == "shabby")

# gdi
gdi_veg_all <- island_veg_all %>% 
  filter(location == "gdi")
```

This is counting how many species each ISLAND has - this does not account for the `NA`s within the dataset, which will need to be addressed later.
```{r}
# # total_island_veg_all_count <- 
#   
# island_veg_all %>%
#   group_by(location) %>% 
#   count(spp) %>%
#   mutate(species_count = n) 
# 
# # %>% 
# #   mutate(n = 1) %>%
# #   count(n) %>% 
# #   mutate(island_count = nn)
# 
# # island_veg_all <- island_veg_all %>% 
# #                   left_join(island_veg_all_count, island_veg, by = "location")
```


# Analysis - Heron

```{r}
heron_veg_all %>% 
ggplot(mapping = aes(x = spp)) + 
  geom_bar() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```

```{r}
contingency_table_heron <- table(heron_veg_all$location, heron_veg_all$spp)
contingency_table_heron
```

```{r}
chisq.test(contingency_table_heron)
```

